### 2018-05-18 manuscript.rmd
update Figure reference

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Figs. \@ref(traitdist),\@ref(fig:median-cont),\@ref(fig:depth-BI)) [@mapstone2014global; @mackie1987siphonophore]. The depth distribution of siphonophore populations is not always static, as some species are known to be vertical migrators, although this is within a relatively narrow depth range (<100m) [@pugh1984diel]. Some species such as *Nanomia bijuga* exhibit synchronous diel migration patterns [@barham1966deep]. Using the present phylogeny, we reconstructed the median depth changes along the phylogeny under a Brownian Motion model (Fig. \@ref(fig:median-cont) and \@ref(fig:depth-BI)), which had the strongest AICc support (compared to non-phylogenetic distributions, and to Ohrnstein-Uhlenbeck). This model indicates a mesopelagic most recent common ancestor, with several independent transition events to epipelagic and bathypelagic waters. There was only a single transition to benthic lifestyle on the branch of Rhodaliidae, and a single transition to a pleustonic lifestyle on the branch of *P. physalis*. There is evidence that habitat depth is conserved within some clades, with the exception of Calycophorae which have diversified across the water column (Fig. \@ref(fig:median-cont), and \@ref(fig:depth-BI)). Under the ML topology, depth appears to be phylogenetically conserved in Euphysonectae after the split between Clade A (shallow-living species) and Group B (deep-dwelling species) (Fig. \@ref(fig:median-cont)), while under the BI-CAT topology, a mesopelagic common ancestor is predicted, with a transition to epipelagic waters in Clade A (Fig. \@ref(fig:depth-BI)); however several shallow-living species that likely belong in Group B were not included in this analysis. The present sampling is also not sufficient to capture significant variation in depth distributions between closely related species. Previous studies have shown that many species that are collected at the same locality are found to occupy discrete, largely non-overlapping depth distributions, including between species that are closely related [@pugh1974vertical]. This suggests that vertical habitat use is more labile than it appears and may be an important mechanism in siphonophore ecology. The observed variation in depth distribution could be attributed to any of the correlated environmental variables (i.e. temperature, chlorophyll, oxygen). Temperature has been hypothesized to impose physiological limits to the dispersal of some clausophyid siphonophores [@grossmann2015diversity]. Since we only have oceanographic data from the Monterey Bay region, our analyses cannot disentangle the effects of these different variables on the vertical distributions.

>>>>

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Fig. \@ref(traitdist), \@ref(fig:median-cont), \@ref(fig:depth-BI)) [@mapstone2014global; @mackie1987siphonophore]. The depth distribution of siphonophore populations is not always static, as some species are known to be vertical migrators, although this is within a relatively narrow depth range (<100m) [@pugh1984diel]. Some species such as *Nanomia bijuga* exhibit synchronous diel migration patterns [@barham1966deep]. Using the present phylogeny, we reconstructed the median depth changes along the phylogeny under a Brownian Motion model (Fig. \@ref(fig:median-cont) and \@ref(fig:depth-BI)), which had the strongest AICc support (compared to non-phylogenetic distributions, and to Ohrnstein-Uhlenbeck). This model indicates a mesopelagic most recent common ancestor, with several independent transition events to epipelagic and bathypelagic waters. There was only a single transition to benthic lifestyle on the branch of Rhodaliidae, and a single transition to a pleustonic lifestyle on the branch of *P. physalis*. There is evidence that habitat depth is conserved within some clades, with the exception of Calycophorae which have diversified across the water column (Fig. \@ref(fig:median-cont), and \@ref(fig:depth-BI)). Under the ML topology, depth appears to be phylogenetically conserved in Euphysonectae after the split between Clade A (shallow-living species) and Group B (deep-dwelling species) (Fig. \@ref(fig:median-cont)), while under the BI-CAT topology, a mesopelagic common ancestor is predicted, with a transition to epipelagic waters in Clade A (Fig. \@ref(fig:depth-BI)); however several shallow-living species that likely belong in Group B were not included in this analysis. The present sampling is also not sufficient to capture significant variation in depth distributions between closely related species. Previous studies have shown that many species that are collected at the same locality are found to occupy discrete, largely non-overlapping depth distributions, including between species that are closely related [@pugh1974vertical]. This suggests that vertical habitat use is more labile than it appears and may be an important mechanism in siphonophore ecology. The observed variation in depth distribution could be attributed to any of the correlated environmental variables (i.e. temperature, chlorophyll, oxygen). Temperature has been hypothesized to impose physiological limits to the dispersal of some clausophyid siphonophores [@grossmann2015diversity]. Since we only have oceanographic data from the Monterey Bay region, our analyses cannot disentangle the effects of these different variables on the vertical distributions.
